---
title: "OxRep Initial Viz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r packages}
library(maps)
library(mapproj)
library(leaflet)
library(rgdal)
library(GISTools)
library(sp)
library(plyr)
library(ggplot2)
library(ggmap)
```

# OxRep Visualisations

This is a set of quick and dirty visualisations for the OxRep project

# Aqueducts

A map of Roman aqueducts was accessed from http://awmc.unc.edu/wordpress/map-files/ and imported into R as follows:

```{r}
aqueducts <- readOGR(dsn = "data/shapefiles/", layer = "aqueducts", verbose = F)
```

An interactive map of the aqueducts can be easily created as follows, note that clicking on the aqueducts will provide popup information.

```{r}
aqueduct_labeller <- function(Name = NA, Source = NA, SHAPE_Leng = NA) {
    paste0(# "<p>", Name, "</p>",
      "<p>Name: ", Name, "</p>",
      "<p>Source: ", Source, "</p>",
      "<p>Length: ", SHAPE_Leng, "</p>")
  }
map <- leaflet(data = aqueducts) %>% addTiles()
map %>% addPolylines(
  popup = ~aqueduct_labeller(Name, Source, SHAPE_Leng)
)
```

# Roman Road Network

I've attempted to visualise the Roman Road Network [1] but have not yet succeeded in correctly formatting the data for display.

[1] - M McCormick et al. 2013 - Roman Road Network (version 2008) [Shapefile], http://darmc.harvard.edu/icb/icb.do?keyword=k40248&pageid=icb.page601659.

```{r}
## Load county borders
roman_roads_shapefile <- readOGR(dsn = "data/shapefiles/", layer = "roman_roads_v2008", verbose = F)
map <- leaflet(data = roman_roads_shapefile) %>% addTiles()
map %>% addPolygons(
  stroke = FALSE,
  smoothFactor = 0.2,
  fillOpacity = 0.8,
  # fillColor = ~ pal(var),
  weight = 1
)
```

# OxRep Locations

```{r}
imported_locations <- read.csv("data/Current OxREP database/locations.csv", stringsAsFactors = F)
oxrep_locations <- imported_locations
## Drop locations at (0,0)
oxrep_locations <- oxrep_locations[oxrep_locations$loclat != 0 & oxrep_locations$loclong != 0,]

oxrep_locations <- oxrep_locations[!is.na(oxrep_locations$loclat) | !is.na(oxrep_locations$loclong),]

```

There are `r nrow(imported_locations[imported_locations$loclat == 0 & imported_locations$loclong == 0,])` locations at coordinates (0,0) which I assume to be nonsense data and so have removed this from the analysis. There are also `r imported_locations[is.na(imported_locations$loclat) | is.na(imported_locations$loclong),] %>% nrow()` rows with NA in the longitude or latitude columns, these have been removed - leaving `r nrow(oxrep_locations)` data points in the dataset.

```{r}
spdf <- SpatialPointsDataFrame(coords = oxrep_locations[,c("loclong", "loclat")], data = oxrep_locations)

oxrep_labeller <- function(locname = NA, loccrdcomment = NA) {
    paste0(# "<p>", Name, "</p>",
      "<p>locname: ", locname, "</p>",
      "<p>loccrdcomment: ", loccrdcomment, "</p>")
  }

map <- leaflet(data = spdf) %>% addTiles()
map %>% addCircles(
  popup = ~oxrep_labeller(locname, loccrdcomment)
)

```


## Shipwrecks

```{r}
data.frame(
  "Name" = "locname",
  "Date Range" = paste0("from",post_0,"to",ante_0),
  
)
```

Switch between terrain and areas...





