---
title: "MEETING NOTES"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## IFRAME 1


### Color switch from country to citations

So a different colour (but with resampling from colour vector) for each citation.

Note that this is almost finished

### Remove the legend for Figure 1

### Figure 1 additional filters

REMOVE INCENTIVE RANGE SLIDER

Repeated vs. One-shot Reporting, [repeated], radio buttons: “Both”, [repeated==1] “Only Repeated”, [repeated==0] “Only One-Shot”

In the Lab vs. Online/Telephone, [remote], radio buttons: “Both”, [remote==0] “Only Lab”, [remote==1] “Only Online/Telephone”

Control Rolls Suggested, [control_rolls], radio buttons: “Both”, [control_rolls==1], “Experimenter Suggested Control Rolls”, [control_rolls==0], “Experimenter did not Suggest Control Rolls”

Reporting Random Draw or State of Mind, [internal_lying], “Both”, [internal_lying==0] “Reporting Random Draw”, [internal_lying==1] “Reporting State of Mind”

True Distribution, [true_distribution_text],  selectize with all options selected as default (this will be about six options)

Radio Button:

```{r}
data_figure1$remote
```

Selectize:

```{r}
data_figure1$true_distribution_text %>% unique()
```

### Figure 1 control tooltips

Add a tooltip similar to that on the ilabour site

"Filter contintents by deleting/adding their names" etc

### Rename "Additional Filters"

"Click here for more filters"

### "Drag to zoom note"

Make it smaller, also add a note that clicking on the bubbles will open the study.

Then remove the tip from the tooltip as wasting space :)

### Figure 2 (Distribution of...)

Change tooltip to be Quartile 1...

y-axis title "Percent"

Remove title of chart (as in the tabPanel)












# 20th March 2017

## iframe 1

Drop continents from the filter, just use country and bring out of the fold.

Order all selectize alphabetically

# In the modal

Have:

- Citation
- Paper Title (new column being added)
- Country
- Number of subjects
- Weblink
