---
title: "Prag Data Visualisations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

# Jonathan's ORCID



# Livian Distribution

Jonathan would like this to be ordered by book, but with an interactive control that allows users to re-order by % of Adriatic etc.

Book names don't exist, they're just numbered.

Preference for highchart for the cleanness.

Jonathan prefers the highchart version.

Jonathan wants ability to switch betweeen % and number of chapters.

```{r import_livian}
livian_dist <- read.csv(file = "livian-distribution.csv")
colnames(livian_dist) <- c("Book","Rome.and.the.West","East.of.the.Adriatic")
livian_dist$Book <- as.factor(livian_dist$Book)
## Convert wide to long with tidr
library(tidyr)
livian_dist_long <- gather(livian_dist, key = "Book", value = "Value")

```


```{r plotly_Livian_barchart}
library(plotly)
plot_ly(data = livian_dist, type = "bar",
        x = Rome.and.the.West,
        y = Book,
        orientation = "h",
        name = "Rome and the West"
        ) %>%
        add_trace(
        data = livian_dist,
        type = "bar",
        x = East.of.the.Adriatic,
        y = Book,
        orientation = "h",
        name = "East of the Adriatic"
        ) %>%
        layout(
        barmode = "stack",
        barnorm = "percent",
        xaxis = list(title = "Percentage"),
        yaxis = list(title = "Book")
        )
```

This is a highchart chart of the livian dist chart you had in Excel

```{r highcharter_livian_dist}
library(highcharter)

selected <- "Rome.and.the.West"


order(livian_dist[,"Rome.and.the.West"] / {livian_dist[,"Rome.and.the.West"] + livian_dist[,"East.of.the.Adriatic"]})


livian_dist[order(livian_dist[,"Rome.and.the.West"]),]



livian_order_by <- function(location){
  livian_dist[rev(order(livian_dist[,location])),]
}

livian_order_by("Rome.and.the.West")


hc <- highchart() %>% 
  hc_xAxis(categories = as.character(livian_dist$Book), title = list(text = "Book")) %>% 
  hc_add_series(name = "Rome and the West", data = livian_dist$Rome.and.the.West) %>% 
  hc_add_series(name = "East of the Adriatic", data = livian_dist$East.of.the.Adriatic)

hc %>% hc_chart(type = "bar") %>% hc_plotOptions(series = list(stacking = "percent"))
```

# Legions

```{r import_legions}
legions_data <- read.csv(file = "legions.csv")
## Make long use tidyr's gather
legions_data_long <- gather(legions_data, key = "Country", value = "Value")
colnames(legions_data_long) <- c("Country","Year","Value")
## Remove preceeding "X" from all values in Year:
legions_data_long$Year <- as.factor(gsub(pattern = "X", replacement = "", legions_data_long$Year))

```

This is a plotly chart of the legions chart you had in Excel

```{r plotly_legions}
legions_east <- legions_data_long[legions_data_long$Country == "East",]
legions_west <- legions_data_long[legions_data_long$Country == "West",] 

plot_ly(data = legions_east, type = "bar",
        x = Year,
        y = Value,
        orientation = "v",
        name = "East"
        ) %>%
  add_trace(data = legions_west, type = "bar",
        x = Year,
        y = Value,
        orientation = "v",
        name = "West"
        ) %>%
  layout(xaxis = list(autorange = "reversed", title = "Date (BC)"),
        yaxis = list(title = "Number of Legions"))
```

This is a highcharter chart of the legions chart you had in Excel

```{r}
legions_east <- legions_data_long[legions_data_long$Country == "East",]
legions_west <- legions_data_long[legions_data_long$Country == "West",] 

hc <- highchart() %>% 
  hc_xAxis(categories = 200:91, 
           # categories = as.character(legions_data_long$Year), 
           title = list(text = "Date (BC)")) %>% 
  hc_add_series(name = "East", data = legions_east$Value) %>% 
  hc_add_series(name = "West", data = legions_west$Value) %>%
  hc_yAxis(title = list(text = "Number of Legions"))

hc %>% hc_chart(type = "column", zoomType = "x")
```

# Triumphs

```{r import_triumps}
triumphs_data <- read.csv(file = "tirumph-frequency.csv")
```

Plotly chart:

```{r plotly_triumphs}
p <- plot_ly(
  data = triumphs_data,
  type = "bar",
  x = Date.BC,
  y = no..of.triumphs,
  orientation = "v",
  name = "Number of triumps per decade",
  width = "100%",
  height = "100%"
  )
  
  p %>% add_trace(x = triumphs_data$Date.BC, y = fitted(loess(
  triumphs_data$no..of.triumphs ~ as.numeric(1:length(levels(
  triumphs_data$Date.BC
  )))
  )),
  name = "loess fit") %>%
    layout(xaxis = list(tickangle=45, title = ""),
           yaxis = list(title = "Number of triumps per decade"),
           margin = list(b=50),
           title = "Number of Triumps per decade from 320 - 50 BC")
```

Highcharter chart:


```{r}

hc <- highchart() %>% 
  hc_xAxis(categories = triumphs_data$Date.BC, 
           title = list(text = "Date in ten year periods (BC)")) %>% 
  hc_add_series(name = "Number of triumps per decade", data = triumphs_data$no..of.triumphs) %>% 
  hc_yAxis(title = list(text = "Number of triumphs per decade"))
hc %>% hc_chart(type = "column", zoomType = "x")
```

