---
title: "Shakespeare Visualisations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r load_libraries}
library(visNetwork)
library(plyr)
library(igraph)
library(jsonlite)
library(rjson)
library(ForceAtlas2)
library(DT)
```


```{r discussions_df_import}
discussions_json <- fromJSON(file = "project-376-comments_2016-05-18.json")

col_1 <- sapply(discussions_json,"[[", 1)
col_2 <- sapply(discussions_json,"[[", 2)
col_3 <- sapply(discussions_json,"[[", 3)
col_4 <- sapply(discussions_json,"[[", 4)
col_5 <- sapply(discussions_json,"[[", 5)
col_6 <- sapply(discussions_json,"[[", 6)
col_7 <- sapply(discussions_json,"[[", 7)
col_8 <- sapply(discussions_json,"[[", 8)
col_9 <- sapply(discussions_json,"[[", 9)
col_10 <- sapply(discussions_json,"[[", 10)
col_11 <- sapply(discussions_json,"[[", 11)
col_12 <- sapply(discussions_json,"[[", 12)

## Unlist lists: http://stackoverflow.com/a/2995515/1659890
col_8[sapply(col_8, is.null)] <- NA
col_8 <- unlist(col_8)
col_9[sapply(col_9, is.null)] <- NA
col_9 <- unlist(col_9)


discussions_df <- data.frame(
  "board_id" = col_1,
  "board_title" = col_2,
  "board_description" = col_3,
  "discussion_id" = col_4,
  "discussion_title" = col_5,
  "comment_id" = col_6,
  "comment_body" = col_7,
  "comment_focus_id" = col_8,
  "comment_focus_type" = col_9,
  "comment_user_id" = col_10,
  "comment_user_login" = col_11,
  "comment_created_at" = col_12,
  check.names = F,
  stringsAsFactors = F
)
```

```{r users_df}
unique_user_ids <- unique(discussions_df$comment_user_id)

unique_user_logins <- unique(discussions_df$comment_user_login)

user_df <- data.frame(
  "n.id" = 1:length(unique_user_ids),
  "comment_user_id" = unique_user_ids,
  "comment_user_login" = unique_user_logins
)
```

```{r discussion_edge_generator}
discussion_edges <- data.frame(
  "from" = as.numeric(),
  "to" = as.numeric(),
  "board_id" = as.numeric(),
  "board_title" = as.character(),
  "board_description" = as.character(),
  "discussion_id" = as.numeric(),
  "discussion_title" = as.character()
)

comment_edges_generator <- function(discussion_id) {
  comments_on_discussion <-
    discussions_df[discussions_df$discussion_id == discussion_id, ]
  
  commenters <- unique(comments_on_discussion$comment_user_id)
  # print(paste0("commenters: ",commenters))
  if (length(commenters) < 2) {
    return()
  } else {
    commenter_combinations <- combn(commenters, 2, simplify = T)
    # print(comments_on_discussion$board_id)
    comment_edges_for_page <- data.frame(
      "from" = commenter_combinations[1, ],
      "to" = commenter_combinations[2, ],
      "board_id" = rep(comments_on_discussion$board_id[1],ncol(commenter_combinations)),
      "board_title" = rep(comments_on_discussion$board_title[1],ncol(commenter_combinations)),
      "board_description" = rep(comments_on_discussion$board_description[1],ncol(commenter_combinations)),
      "discussion_id" = rep(comments_on_discussion$discussion_id[1],ncol(commenter_combinations)),
      "discussion_title" = rep(comments_on_discussion$discussion_title[1],ncol(commenter_combinations)),
      stringsAsFactors = F
    )
    comment_edges_for_page
    
    # if (length(commenters) == 1) {
    #   comment_edges_for_page <- data.frame(
    #     "from" = commenters,
    #     "to" = commenters,
    #     "board_id" = comments_on_discussion$board_id,
    #     "board_title" = comments_on_discussion$board_title,
    #     "board_description" = comments_on_discussion$board_description,
    #     "discussion_id" = comments_on_discussion$discussion_id,
    #     "discussion_title" = comments_on_discussion$discussion_title
    #   )
    #   comment_edges_for_page
  }
}

### Apply the function:

invisible(lapply(unique(discussions_df$discussion_id), function(x) {
  discussion_edges <<-
    rbind(discussion_edges, comment_edges_generator(x))
}))
```

# Discussion Network

The size of the discussion network is large, there are `r length(user_df$comment_user_id)` individual comments and a total of `r nrow(discussion_edges)` interactions between commenters. An interaction is considered as follows:

- All commenters on a discussion are considered to have interacted with one another (i.e. a complete graph is formed from the list of commenters on a discussion page)

For indicative purposes, a static visualisation of the total network is displayed below (force atlass 2 layout)

```{r force_atlas, include=FALSE}
g <- graph.data.frame(discussion_edges[,c(1,2)], directed = F)
invisible(forceatlas_layout <- layout.forceatlas2(graph = g, iterations = 200))
```


```{r entire_network_igraph}
plot(g, vertex.size = 5, vertex.label = "", layout = forceatlas_layout, edge.width = .7)
```

The distribution of data across the 9 boards is as follows:

```{r table_of_boards}
# Get name of boards
boards_vector <- names(table(discussion_edges$board_title))
# Tally edges
board_edges_tally <- as.numeric(table(discussion_edges$board_title))[order(boards_vector)]



# Tally commenters
commenters_per_board <- function(board_name) {
  sample <-
  discussion_edges[discussion_edges$board_title == board_name, ]
  length(unique(c(sample$from, sample$to)))
}
board_commenters_tally <- unlist(lapply(boards_vector, function(x)commenters_per_board(x)))
# Tally discussions
discussions_per_board <- function(board_name) {
  sample <-
  discussion_edges[discussion_edges$board_title == board_name, ]
  length(unique(sample$discussion_title))
}
board_discussions_tally <- unlist(lapply(boards_vector, function(x)discussions_per_board(x)))

board_summary <- data.frame(
  "Board Name" = boards_vector,
  "Discussions in Board" = board_discussions_tally,
  "Commenters in Board" = board_commenters_tally,
  "Edges in Board" = board_edges_tally
)
DT::datatable(board_summary)
```

The largest board is visualised as follows:

```{r board_specific_graph_attrs}
board_specific_edges <- function(board = NA){
  board_specific_edges <- discussion_edges[discussion_edges$board_title == board,]
}

board_specific_nodes <- function(board = NA){
  board_specific_edges <- discussion_edges[discussion_edges$board_title == board,]
  user_df[user_df$comment_user_id %in% unique(c(board_specific_edges$from, board_specific_edges$to)),]
}
```

```{r notes_visNetwork}
notes_edges <- board_specific_edges("Notes")
notes_nodes <- board_specific_nodes("Notes")


visN_edges <- data.frame(
  "from" = notes_edges$from,
  "to" = notes_edges$to,
  "title" = notes_edges$discussion_title
)

visN_nodes <- data.frame(
  "id" = notes_nodes$comment_user_id,
  "title" = notes_nodes$comment_user_login,
  "label" = notes_nodes$comment_user_login
)

visNetwork(nodes = visN_nodes, edges = visN_edges) %>%
  visIgraphLayout(layout = "layout_on_sphere")
```

# Help & Technical Issues

```{r}
help_edges <- board_specific_edges("Help and Technical issues")
help_nodes <- board_specific_nodes("Help and Technical issues")

visN_edges <- data.frame(
  "from" = help_edges$from,
  "to" = help_edges$to,
  "title" = help_edges$discussion_title
)

visN_nodes <- data.frame(
  "id" = help_nodes$comment_user_id,
  "title" = help_nodes$comment_user_login,
  "label" = help_nodes$comment_user_login
)

visNetwork(nodes = visN_nodes, edges = visN_edges) %>%
  visIgraphLayout(layout = "layout_with_lgl")
```


# Women

The "Women writers and autobiography" network appears as follows:

```{r women_writers_visNetwork}

women_writers_edges <- discussion_edges[discussion_edges$board_title == "Women writers and Autobiography",]

women_writers_nodes <- user_df[user_df$comment_user_id %in% unique(c(women_writers_edges$from, women_writers_edges$to)),]

visN_edges <- data.frame(
  "from" = women_writers_edges$from,
  "to" = women_writers_edges$to,
  "title" = women_writers_edges$discussion_title
)

visN_nodes <- data.frame(
  "id" = women_writers_nodes$comment_user_id,
  "title" = women_writers_nodes$comment_user_login,
  "label" = women_writers_nodes$comment_user_login
)

visNetwork(nodes = visN_nodes, edges = visN_edges) %>%
  visIgraphLayout()
```





